---
title: "The Air Quality Dataset"
author: "Johnson W. Ahiadorme"
date: "6/12/2019"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Summary of Air Quality Dataset

This exercise will be working with the built-in ```air quality``` dataset.^[ Chambers, J. M., Cleveland, W. S., Kleiner, B. and Tukey, P. A. (1983) Graphical Methods for Data Analysis. Belmont, CA: Wadsworth.] This dataset contains 154 daily air quality measurements in New York from May 1, 1973 (a Tuesday) to September 30, 1973. The dataset contains 6 variables:

- **Ozone**: Mean ozone in parts per billion _(ppb)_ from 1300 to 1500 hours at Roosevelt Island;
- **Solar.R**: Solar radiation in Langleys _(lang)_ in the frequency band 4000–7700 Angstroms from 0800 to 1200 hours at Central Park;
- **Wind**: Average wind speed in miles per hour _(mph)_ at 0700 and 1000 hours at LaGuardia Airport;
- **Temp**: Maximum daily temperature in degrees Fahrenheit _(oF)_ at LaGuardia Airport;
- **Month**: numeric month _(1-12)_
**Day**: numeric Day of the month _(1-31)_

Here is a summary of the data


```{r airquality}
summary(airquality)
```

### Table of Top of the Air Quality Dataset

A table of the head of the air quality dataset 

```{r}
knitr::kable(head(airquality),
             caption = "Top of the Air Quality 
             Dataset")
```

### Plot of Ozone by Temperature –Air Quality Dataset

A plot of the temperature and ozone from the built-in air quality dataset 

```{r}
plot(airquality$Temp, airquality$Ozone, 
     main = "Airquality: Ozone by Temperature")
```



